### 2021-09-27 paper/main.tex
Add render

%\usepackage{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
\usepackage{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\newcommand{\gilles}[1]{\textcolor{orange}{GL: #1}}
\newcommand{\antoine}[1]{\textcolor{green}{AW: #1}}
\newcommand{\joeri}[1]{\textcolor{red}{JH: #1}}
\newcommand{\arnaud}[1]{\textcolor{blue}{AD: #1}}
\newcommand{\old}[1]{\textcolor{magenta}}

@@

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
\runningtitle{Towards Drawing Scientific Conclusions with Simulation-Based Inference }

@@

\begin{abstract}

%   In recent years a myriad of simulation-based inference algorithms have been developed
%   with the objective to produce approximations as close as possible to the ground truth.
%   In this work we take the position that minimizing a divergence between the approximation and an unknown ground truth can incorrectly drive scientific inquiry. Instead, we argue for conservativeness. Approximations should therefore always convey at least as much uncertainty as the ground truth, and never be overconfident. We assess conservativeness by measuring coverage and showcase through extensive experiments that various approaches in simulation-based inference can produce non-conservative posterior estimators. We show empirically that ensembles consistently help in this regard but can still lead to non-conservative posterior estimators. Finally, we discuss several perspectives and open avenues of research towards conservative estimators.

% My pass:
%
%
%Computer simulators are at the center of many scientific disciplines.
%Although modern simulators are able to describe complex processes, they are less suited
%for statistical inference. 
%At the core of this problem lies the intractable likelihood model implicitly defined by the simulator's computer code. 
%To deal with this intractability,
%a myriad of Bayesian inference algorithms have been developed to approximate
%posteriors as possible to their unknown ground truths. The only requirement of these algorithms being that generating simulations is possible.
%In this work, we take the position that minimizing a divergence between the approximation and an unknown ground truth can incorrectly drive scientific inquiry. Instead, we
%argue for conservative approximations, meaning that they should always convey at least as much uncertainty as the ground truth. We collect extensive
%empirical evidence spanning months of computation on several computer clusters. Our results indicate that all benchmarked techniques produce non-conservative posterior
%approximations. Complicating their applicability.
%We show that ensembles are consistently more reliable in this regard, but can still lead to non-conservative
%estimators. Our study is complemented with new research proposals to strengthen the
%application of simulation-based inference in the sciences.

%\joeri{Reworked Gilles' proposal a bit. See below.}

% 
% Joeri's proposal after Gilles' proposal
%
%

%Recent years have seen tremendous innovations in the field of Bayesian simulation-based inference.
%{\color{blue} This work takes a step back by assessing the reliability of these algorithms to scientific use-cases concerned with constraining parameters, as is often the case in the physical sciences.??? We present...}
%This work presents extensive empirical evidence that all benchmarked algorithms -- including \textsc{(s)nre}, \textsc{(s)npe}, \textsc{snl} and various forms of \textsc{abc} -- produce non-conservative posterior approximations. Making these algorithms demonstrably unreliable if one's scientific goal is to constrain parameters of interest, as is often the case in the physical sciences. Our results further demonstrate that ensembles are consistently more reliable in this regard, although they may still lead to non-conservative posterior approximations.
%We argue that failing to address this issue will lead to a well-founded distrust in simulation-based inference. For this reason we argue that research efforts should now focus on theoretical and methodological advances to guarantee conservative approximate inference.

%
% Gilles proposal
%
We present extensive empirical evidence showing that current Bayesian simulation-based inference algorithms are inadequate for the falsificationist methodology of scientific inquiry.
Our results collected through massive experimental computations show that all benchmarked algorithms -- \textsc{(s)npe}, \textsc{(s)nre}, \textsc{snl} and variants of \textsc{abc} -- may produce overconfident posterior approximations, which makes them demonstrably unreliable and dangerous if one's scientific goal is to constrain parameters of interest. %, as is often the case in the physical sciences.
We believe that failing to address this issue will lead to a well-founded trust crisis in simulation-based inference.
For this reason, we argue that research efforts should now focus on theoretical and methodological developments of conservative approximate inference algorithms and present research directions towards this objective.
In this regard, we show empirical evidence that ensembles are consistently more reliable.

% \\\joeri{Which version? Merge?}

% In recent years a myriad of simulation-based inference algorithms have been developed to perform Bayesian inference with an intractable likelihood implicitly defined by a simulator. Those algorithms traditionally have as objective to produce approximate posterior over the quantity to be inferred as close as possible to the ground truth posterior. In this work, we take the position that minimizing a divergence between the approximation and an unknown ground truth can lead to overconfident approximations and hence incorrectly drive scientific inquiry. Instead, we argue for conservativeness meaning that approximations should therefore always convey at least as much uncertainty as the ground truth, and never be overconfident. Our main contribution lies in the generation through month of computation of extensive empirical evidence that all currently existing approaches in simulation-based inference can produce non-conservative posterior estimators and are hence not suited for scientific purpose as they are. We show empirically that ensembles consistently help in this regard but can still lead to non-conservative posterior estimators and discuss several perspectives and open avenues of research towards conservative estimators.

@@

% Many scientific disciplines rely on computer simulations to study complex phenomena under various conditions. 
% Although modern simulators can generate realistic synthetic observables through detailed descriptions of their data generating processes, 
% they are unfortunately not suitable for statistical inference.
% At the core of this issue lies the likelihood model $p(\vx\vert\vtheta)$ implicitly defined by 
% computer code describing the data generating processes.
% The direct evaluation of the likelihood rests on the \emph{intractable} integration of all stochastic execution paths, rendering statistical inference based on the likelihood impractical.
% Fortunately, inference remains possible by relying on likelihood-free \emph{approximations} \citep{cranmer2020frontier}
% within a field referred to as simulation-based or likelihood-free inference.

@@

In this work, we measure the quality of the credible regions computed through various Bayesian techniques in simulation-based inference and do so through the notion of \emph{coverage}. 
We frame our main contribution as the collection of extensive empirical evidence that required months of computation. 
Our results demonstrate that all benchmarked techniques can produce non-conservative credible regions, highlighting the need for a new class of conservative approximate inference algorithms.
The structure of the paper is outlined as follows.
Section \ref{sec:background} describes the statistical formalism, necessary background and includes a thorough motivation for coverage.
Section \ref{sec:experiments} highlights our main results.
Section \ref{sec:discussion} presents several avenues of future research to {\bfseries enable drawing reliable scientific conclusions} with simulation-based inference. All code related to this manuscript is available at
\href{https://github.com/anonymous/anonymous}{\texttt{github.com/anonymous/anonymous}}.
%\href{https://github.com/JoeriHermans/troubles-in-paradise}{\texttt{github.com/montefiore-ai/troubles-in-paradise}}

%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, the natural sciences make decisions based on frequentist confidence intervals or Bayesian credible regions.

%Although simulation-based inference targets domain sciences, advances in the field are mainly driven from a machine learning perspective.
%The field therefore inherits the quality assessments \citep{lueckmann2021benchmarking} customary to the machine learning literature which usually involves maximizing some criterion. Despite recent developments of post hoc diagnostics to inspect the quality of likelihood-free approximations \citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking, sbc, dalmasso2020confidence}, the problem concerning \emph{scientific conclusions} based on simulation-based inference remains: \emph{can these techniques be used to drive scientific research whenever their fitting criteria are not globally optimized or the availability of data is limited?}

%{\bfseries sciences are rather concerned with
%\emph{excluding} hypotheses at some confidence level}

%As an illustration of this, a recent application consist in inferring the nature (cold or warm) and mass of dark matter through the observation of the evolution of stellar streams' density. The simulator evolves a stream and its stellar density through a stochastic iterative process though interactions with a family of dark matter subhaloes parametrized though the mass of the dark matter \arnaud{where does the nature appear?}. The iterative nature of the simulator leads to an intractable likelihood since evaluating it would require to consider all execution paths. \joeri{Rewrite}

%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, the natural {\bfseries sciences are rather concerned with
%\emph{excluding} hypotheses at some confidence level}
%While the majority of machine learning literature targets to \emph{maximize} a criterion such as accuracy or likelihood with the objective of obtaining the best fit, a common concern in natural {\bfseries sciences is rather to \emph{exclude} hypotheses at some confidence level}.

%For this reason, domain scientists want guarantees to whether statistical \emph{approximations} have confidence intervals (frequentist) or credible regions (Bayesian) not smaller than they should be. In this work we adopt the Bayesian point of view, and are then concerned with not rejecting viable parameters from the credible region and incorrectly drive scientific inquiry.
%If that would \emph{not} be the case, scientists could reject viable hypotheses and incorrectly drive scientific inquiry.

%Considering the example of the inference of the nature and mass of dark matter based on the observation of a stellar streams, incorrectly inferring the nature can have a disastrous cascading effects. Those can be found in the field of particle physics where excluding warm dark matter would exclude the hypothesized sterile neutrino. \arnaud{refs} On the contrary, if cold dark matter were to be excluded, the theory for the disruptions of stellar streams would not hold.

%{\bfseries what guarantees or properties do these techniques have whenever their fitting criteria are not globally optimized or the availability of data is limited?}

% Every result and figure is annotated with \code{https://github.com/montefiore-ai/troubles-in-paradise}, linking to the code used to generate it.

%Despite recent methodological developments~\gilles{refs} and successes across various scientific use cases~\gilles{refs}, a major criticism of simulation-based inference is that the involved statistical computations are essentially not verifiable and are therefore not suitable for scientific disciplines whose primary objective is to \emph{constrain} parameters of interest, or \emph{exclude} models at a certain confidence level.

%We emphasize that algorithms should not just show high performances \arnaud{rephrase}. In the case of Bayesian posterior inference, domain scientists should also have guarantees that credible regions identified with approximate posteriors are not smaller than they should be, since rejecting parameter values compatible with the data will drive the scientific inquiry to wrong conclusions. \arnaud{this is the case with ... concrete example, gw, streams and refs}

%These concerns have led to further work focusing on improving the accuracy of inference procedures~\gilles{refs} and to the development of post hoc diagnostics to inspect the quality of their approximations~\citep{cranmer2015approximating, Brehmer:2018eca, brehmer2019mining, Hermans:2020skz, lueckmann2021benchmarking}.
%Despite these innovations, it remains unanswered what formal guarantees these techniques have whenever their approximations are not optimal, or equivalently, whenever their fitting criteria are not globally optimized.

%Theoretical characterizations of simulation-based techniques are critically needed to draw scientific conclusions reliably. 
%In this work, we study the empirical coverage of various simulation-based inference techniques over multiple benchmarks and first demonstrate that all those techniques may lead to credible regions that are too narrow with respect to the ground truth, hence leading to Type-I errors and possibly to wrong scientific conclusions. 
%We argue that model regularization constitutes a potential solution and provide a critical discussion about the ability to diagnose such pathologies. The paper is outlined as follows. \arnaud{Update paper structure} Section~\ref{sec:background} outlines the statistical formalism and the necessary background of simulation-based inference. We briefly highlight the importance of a proper diagnostic to inspect the statistical quality of the approximations. Section~\ref{sec:method} outlines our theoretical results and proposed methodology, supported by experimental validation in Section~\ref{sec:experiments}.
\section{Background}
\label{sec:background}

@@

%which can either be the posterior itself. Or the likelihood-to-evidence ratio 
%$$r(x\vert\vartheta) = \frac{p(x \vert \vartheta)}{p(x)}.$$ 
%Through approximations $\hat{r}(x\vert\vartheta)$, evaluating estimates of the posterior density function amount to computing the product of the \emph{tractable} prior probability $p(\vartheta)$ and the estimated likelihood-to-evidence ratio $\hat{r}(x\vert\vartheta)$. An unormalized approximate of the posterior can also be recovered from a surrogate for the likelihood by multiplying it to the prior probability.

%\subsection{Likelihood-free inference methods}
\subsection{Statistical quality assessment}
%The work of \citet{lueckmann2021benchmarking} benchmarks common simulation-based
%techniques on various metrics. Although the benchmarks are done very thoroughly with respect to the \emph{selected} metrics, 
%there are issues regarding their \emph{applicability}.

\begin{figure}[b!]
    \centering
    \includegraphics[width=\linewidth]{figures/auc-deceitful.pdf}
    \caption{A classifier-based metric measures the divergence between posterior approximations and a ground truth by means of evaluating the classifier's discriminative performance through Area Under the Receiver Operating Characteristics curve (\textsc{auroc}). In this case, the metric argues that both the conservative and overconfident approximations are equally accurate since the metric yields \textsc{auroc} = 0.7 for both approximations. From an inference perspective however, the conservative approximation is clearly more suitable because it produces credible regions larger than they should be.}
    \label{fig:auc_deceitful}
\end{figure}
The main problem with metrics such as the Classifier Two-sample Test \citep{lehmann2006testing,lopez2016revisiting} or Maximum Mean Discrepancy \citep{gretton2012kernel,bengio2013bounding,dziugaite2015training} is that they assess \emph{accuracy} or \emph{closeness} of an approximation through a divergence with respect to a posterior that is intractable in practice.
Even if such evaluations would hypothetically be possible,
there are no criteria to what constitutes an \emph{acceptable} estimator.
%for scientific use-cases.
In addition, it is not possible to know for certain whether the classifier or kernel used to measure the diverge are sufficiently expressive to detect differences between the approximation and said posterior.

@@

Instead of measuring accuracy of approximations with respect to an intractable posterior, this work directly probes
the quality of credible regions through \emph{coverage}: a quantity that can be estimated in practice and has a criterion to determine acceptable approximations.
\begin{definition}
The {\bfseries coverage probability} of a posterior estimator at a confidence coefficient $1 - \alpha$ is
\begin{equation}
    \int_{\vtheta}\int_{\vx} p(\vtheta,\vx)~\mathbb{1}\left[\vtheta \in \Theta_{\hat{p}(\vtheta|\vx = \vx)}(1 - \alpha)\right]~\d\vtheta\d\vx,
\end{equation}
where the function
$\Theta_{p(\vtheta\vert\vx)}(1 - \alpha)$ yields the $1 - \alpha$ highest posterior density region
of $\hat{p}(\vtheta\vert\vx)$.
%\begin{equation}
%\mathbb{E}_{(\vtheta^*, \vx_o) \sim p(\vtheta, \vx)} \left\{ \begin{array}{ll}
%    1 & \text{if } \vtheta^* \in \Theta_{\hat{p}(\vtheta|\vx = \vx_o)}(1 - \alpha) \\
%    0 & \text{otherwise}
%\end{array} \right..
%\end{equation}
\end{definition}
\begin{definition}
The {\bfseries empirical coverage probability} of a posterior estimator at a confidence coefficient $1 - \alpha$ given a set of $n$ i.i.d. samples $(\vtheta^*,\vx)\sim p(\vtheta,\vx)$
is
\begin{equation}
\frac{1}{n} \sum_{i=1}^n ~\mathbb{1}\left[\vtheta^*_i \in \Theta_{\hat{p}(\vtheta|\vx = \vx_i)}(1 - \alpha)\right].
\end{equation}
\end{definition}
\begin{definition}
The {\bfseries nominal coverage probability} is the coverage probability of the true posterior and is equal to the known confidence level $(1 - \alpha)\cdot 100\%$.
\end{definition}
\begin{definition}
A posterior estimator is deemed acceptable if it {\bfseries has coverage} at the confidence level of interest, i.e., whenever the empirical coverage probability is {\bfseries larger or equal} to the nominal coverage probability.
\end{definition}
\begin{definition}
A {\bfseries conservative estimator} is an estimator that has coverage for {\bfseries all} confidence levels.
\end{definition}
% \begin{definition}
% The {empirical \bfseries coverage probability} of a posterior estimator at a confidence level $1 - \alpha$ given a set of $n$ i.i.d. samples $(\vtheta^*,\vx)\sim p(\vtheta,\vx)$
% is
% \begin{equation}
% \frac{1}{n} \sum_{i=1}^n \left\{ \begin{array}{ll}
%     1 & \text{if } \vtheta^*_i \in \Theta_i \\
%     0 & \text{otherwise}
% \end{array} \right.,
% \end{equation}
% where $\Theta_i$ is the credible region computed through the posterior approximation $\hat{p}(\vtheta\vert\vx=\vx_i)$ considering that $\vx_i \sim p(\vx\vert\vtheta = \vtheta^*_i)$.
% \end{definition}
% \begin{definition}
% The {\bfseries nominal coverage probability} is effectively equal to the confidence level.
% \end{definition}
% \begin{definition}
% An estimator is deemed acceptable if it {\bfseries has coverage} at the confidence level of interest. That is, whenever the empirical coverage probability is {\bfseries larger or equal} to the nominal coverage probability.
% \end{definition}
% \begin{definition}
% A {\bfseries conservative estimator} is an estimator that has coverage for {\bfseries all} confidence levels.
% \end{definition}
Although coverage is a necessary metric to assess conservativeness, it is limited in its ability to determine the information gain a posterior (approximation) has over its prior. To clarify this point, consider an estimator whose posteriors are identical to the prior. In this case, there is no gain in information and the empirical coverage probability is equal to the nominal coverage probability. For this reason, a complete analysis should be complemented with measures such as the mutual information or expected information gain $\mathbb{E}_{p(\vtheta,\vx)}\left[\log p(\vtheta\vert\vx) - \log p(\vtheta)\right]$.
This work however is concerned with {\bfseries conservative inference} and will therefore limit the analysis to the evaluation of coverage. Finally, it should be noted that coverage is a statement about the credible regions in expectation. Coverage does not make any statement about the quality of a single posterior.

\section{Experimental observations}
\label{sec:experiments}
This section covers our main contribution: the collection of empirical evidence to determine whether approaches in simulation-based inference are conservative by nature. 
We are particularly interested in determining \emph{if} certain approaches should be
favoured over others. We do so by measuring the coverage of estimators attained by these approaches across a broad range of hyperparameters and benchmarks of varied complexity, including two \emph{real} problems from the field of astronomy.
As in real use-cases, the true posteriors associated with these benchmarks are unknown.
Hyperparameters are listed in Appendix \ref{appendix:hyperparameters}.
\subsection{Methods}
\label{sec:methods}
We make the distinction between two paradigms.
Non-amortized approaches are designed to approximate a \emph{single} posterior, while amortized methods aim to learn a general purpose estimator that attempts to approximate \emph{all} posteriors supported by the prior. 
\subsubsection{Amortized}
%from  posterior $p(\vartheta|x_0)$ for an observable $x_0$. Candidates parameters $\vartheta_i$ are first sampled from the prior, $p(\vartheta)$. Those parameters are then used along with the simulator to produce observations $x_i$. The candidate parameters that have produced the closest observations to the target observation $x_0$ according to some distance metric are kept and considered samples from the posterior, $p(\vartheta|x_0)$. \arnaud{add details?: norm 2 distance + quantile 0.01 with at least 100 samples?}  
%Sequential Monte-Carlo ABC (SMC-ABC) \citep{10.1093/bioinformatics/btp619, sisson2007sequential, beaumont2009adaptive} iteratively update a set of particules to match the posterior distribution. At each iteration, candidate parameters that produced the highest distance are discarded and new candidates are generated by adding a perturbation to the remaining candidates. \arnaud{double check that this is correct}
{\bf Neural Posterior Estimation} (\npe) is concerned with directly learning an amortized estimator $\hat{p}_\psi(\vtheta\vert \vx)$ to the posterior with normalizing flows. Normalizing flows define a class of probability distributions $p_\psi(\cdot)$ built from neural network based bijective transformations \citep{dinh2014nice,dinh2016density} parameterized by $\psi$ and are usually optimized via
$\argmin_\psi \mathbb{E}_{p(\vx)} \left[\textsc{kl}(p(\vtheta|\vx)~\vert\vert ~\hat{p}_\psi(\vtheta|\vx)\right]$,
which is equivalent to $\argmax_\psi \mathbb{E}_{p(\vtheta,\vx)}\left[\log \hat{p}_\psi(\vtheta|\vx)\right]$.
Once trained, the density of the modeled distribution can easily be evaluated \emph{and} sampled from.

@@

{\bf Ensembles} An ensemble model \emph{averages} the approximated posteriors of $n$ separately trained posterior estimators. While this formulation is natural for \textsc{npe}, averaging likelihood-to-evidence ratios is equivalent, because
\begin{equation}
    \frac{p(\vtheta)}{n} \sum_{i=1}^n \hat{r}_i(\vx \vert \vtheta) = \frac{1}{n}\sum_{i=1}^n \hat{p}_i(\vtheta \vert \vx).
\end{equation}
\subsubsection{Non-amortized}
Rejection {\bf Approximate Bayesian Computation} \textsc{(abc)} \citep{rubin1984,pritchard1999population}
numerically estimates a \emph{single} posterior by collecting samples $\vtheta\sim p(\vtheta)$ whenever
$\vx\sim p(\vx\vert\vtheta)$ is \emph{similar} to $\vx_o$. Similarity is expressed by means of a \emph{distance function} $\rho$. For high-dimensional observables, the probability of simulating an observable $\vx$ such that $\vx = \vx_o$ is extremely small. For this reason, \textsc{abc} uses a \emph{summary statistic} $s$ and an \emph{acceptance threshold} $\epsilon$. Using these components, \textsc{abc} accepts samples into the approximate posterior whenever $\rho(s(\vx),s(\vx_o))\leq\epsilon$. In our experiments we use the identity function as a sufficient summary statistic. Finally, we emphasize that 
\textsc{abc} approximations are \emph{only exact} whenever the summary statistic is sufficient \emph{and} the acceptance threshold $\epsilon$ tends to 0 \citep{sisson2018overview}.
% Note that
% amortized estimates of the likelihood-to-evidence ratio $r(x\vert\vartheta)$ can be computed through $\hat{p}_\psi(\vartheta\vert x)$ because
% $\log r(x\vert\vartheta) \approx \log \hat{p}_\psi(\vartheta\vert x) - \log p(\vartheta)$. Therefore, the binary discriminator $\hat{d}(\vartheta,x)\triangleq\sigmoid(\log\hat{p}_\psi(\vartheta\vert x) - \log p(\vartheta))$ enables $\hat{p}_\psi(\vartheta,x)$ to be {\bf learned by minimizing
% the binary cross entropy criterion} presented above. All flow-based estimators in this work are optimized using the aforementioned criterion unless stated otherwise.
% \joeri{We can remove this right? Yes my bad}
% Once trained, we can sample new data points from the modeled distribution as well as evaluate the density of new data points. We highlight two possibilities for building an approximate amortized posterior $p_\psi(\vartheta|x)$ with NFs. First, by direct minimization of the \textsc{kl} divergence between the approximate posterior and the actual posterior,
% \begin{align}
%     \psi^* &= \argmin_\psi \mathbb{E}_{p(x)}\left[\textsc{kl}(p(\vartheta|x)~\vert\vert ~p_\psi(\vartheta|x)\right] = \argmin_\psi \mathbb{E}_{p(x)}\mathbb{E}_{p(\vartheta|x)}\left[\log\frac{ p(\vartheta|x)}{p_\psi(\vartheta|x)}\right]\\
%     &= \argmax_\psi \mathbb{E}_{p(\vartheta,x)}\left[\log p_\psi(\vartheta|x)\right].
% \end{align}
% \antoine{Say it is equivalent to MLE. (amortized over posteriors)}
% The second option is to define the NF likelihood-to-evidence ratio as 
% \begin{align}
%     r_\psi(x|\vartheta) := \frac{p_\psi(\vartheta|x)}{p(\vartheta)},
% \end{align}
% and to train it as a classifier-based amortized ratio estimator.
% \antoine{Add the two training methods have the same optimum but the second may be tuned to be blablabla as shown later}
% \joeri{My take below?}

%{\bfseries Sequential methods} aim at estimating the posterior for a specific observable $x_o$ by dedicating the simulation budget to iteratively improve an approximation.
%These methods alternate between a training and a simulation phase, the latter being designed to take \emph{current} knowledge into account such that subsequent simulation parameters $\vartheta$ are expected to produce observables $x$ closer to $x_o$ compared to previous iterations.

@@

\subsection{Results}
\begin{figure*}[h!]
    \includegraphics[width=\textwidth]{figures/coverage_multi.pdf}
    \caption{Evolution of the coverage w.r.t simulation budget. A perfectly calibrated posterior has an empirical coverage probability equal to the nominal coverage probability and produces a diagonal line. Conservative estimators on the other hand produce curves above the diagonal and overconfident models underneath. All algorithms can lead to non-conservative estimators, this pathology tends to be accentuated for small simulation budgets and non-amortized methods.
    Finally, the intractable results indicate that the computational requirements did not allow for a coverage analysis. In the case of \textsc{snl}, this was mostly due to the high dimensional observables. We did not train an embedding network as that is outside of the scope of this work. For the astronomy applications, the simulation model was simply too expensive to reasonable evaluate coverage for non-amortized methods.
    }
    \label{fig:all_coverage_levels}
\end{figure*}
\begin{figure*}[h!]
    %\includegraphics[width=\textwidth]{figures/coverage_multi_ensemble.pdf}
    \includegraphics[width=\textwidth]{figures/coverage_multi_ensemble_with_bagging.pdf}
    \caption{Analysis of coverage between ensemble and individual models w.r.t various simulation budgets. The blue line represents the mean coverage of individual models over 5 runs, the shaded area represents its standard deviation. The black line represents the coverage of a single ensemble composed of 5 models. We observe that ensembles consistently have a higher empirical coverage probability compared to the average individual model. A similar effect is not always observed with bagging, indicated by the red line. Ensembles are only considered on amortized approached due to computational requirements inherent to non-amortized approaches.}
    \label{fig:coverage_ensemble}
\end{figure*}
Figures \ref{fig:all_coverage_levels} and \ref{fig:coverage_ensemble} highlight our main results. Through these plots we can directly assess the \emph{conservativeness} at a given confidence level and simulation budget. The figures should be interpreted as follows: a \emph{perfectly calibrated} posterior has an empirical coverage probability equal to the nominal coverage probability and therefore the known confidence level. Plotting this relation produces a diagonal line. Conservative estimators on the other hand produce curves above the diagonal and overconfident models underneath.
The plots highlight an unsettling observation: {\bfseries all} benchmarked approaches produce non-conservative posterior approximations. In general, this pathology is especially prominent in non-amortized approaches with a small simulation budget. A regime they have been specifically designed for. However, a large simulation budget does not guarantee conservativeness either.

>>>>

%\usepackage{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
\usepackage[accepted]{aistats2022}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

@@

% If your paper is accepted and the title of your paper is very long,
% the style will print as headings an error message. Use the following
% command to supply a shorter title of your paper so that it can be
% used as headings.
%
\runningtitle{Towards Drawing Scientific Conclusions with Simulation-Based Inference}

@@

\begin{abstract}
We present extensive empirical evidence showing that current Bayesian simulation-based inference algorithms are inadequate for the falsificationist methodology of scientific inquiry.
Our results collected through massive experimental computations show that all benchmarked algorithms -- \textsc{(s)npe}, \textsc{(s)nre}, \textsc{snl} and variants of \textsc{abc} -- may produce overconfident posterior approximations, which makes them demonstrably unreliable and dangerous if one's scientific goal is to constrain parameters of interest. %, as is often the case in the physical sciences.
We believe that failing to address this issue will lead to a well-founded trust crisis in simulation-based inference.
For this reason, we argue that research efforts should now focus on theoretical and methodological developments of conservative approximate inference algorithms and present research directions towards this objective.
In this regard, we show empirical evidence that ensembles are consistently more reliable.

@@

@@

In this work, we measure the quality of the credible regions computed through various Bayesian techniques in simulation-based inference and do so through the notion of \emph{coverage}.
We frame our main contribution as the collection of extensive empirical evidence that required months of computation.
Our results demonstrate that all benchmarked techniques can produce non-conservative credible regions, highlighting the need for a new class of conservative approximate inference algorithms.
The structure of the paper is outlined as follows.
Section \ref{sec:background} describes the statistical formalism, necessary background and includes a thorough motivation for coverage.
Section \ref{sec:experiments} highlights our main results.
Section \ref{sec:discussion} presents several avenues of future research to {\bfseries enable drawing reliable scientific conclusions} with simulation-based inference. All code related to this manuscript is available at
\href{https://github.com/montefiore-ai/crisis-in-sbi}{\texttt{github.com/montefiore-ai/crisis-in-sbi}}
\section{Background}
\label{sec:background}

@@

\subsection{Statistical quality assessment}
\begin{figure}[b!]
    \centering
    \includegraphics[width=\linewidth]{figures/auc-deceitful.pdf}
    \caption{A classifier-based metric measures the divergence between posterior approximations and a ground truth by means of evaluating the classifier's discriminative performance through Area Under the Receiver Operating Characteristics curve (\textsc{auroc}). In this case, the metric argues that both the conservative and overconfident approximations are equally accurate since the metric yields \textsc{auroc} = 0.7 for both approximations. From an inference perspective however, the conservative approximation is clearly more suitable because it produces credible regions larger than they should be.}
    \label{fig:auc_deceitful}
\end{figure}
The main problem with metrics such as the Classifier Two-sample Test \citep{lehmann2006testing,lopez2016revisiting} or Maximum Mean Discrepancy \citep{gretton2012kernel,bengio2013bounding,dziugaite2015training} is that they assess \emph{accuracy} or \emph{closeness} of an approximation through a divergence with respect to a posterior that is intractable in practice.
Even if such evaluations would hypothetically be possible,
there are no criteria to what constitutes an \emph{acceptable}
In addition, it is not possible to know for certain whether the classifier or kernel used to measure the diverge are sufficiently expressive to detect differences between the approximation and said posterior.

@@

Instead of measuring accuracy of approximations with respect to an intractable posterior, this work directly probes
the quality of credible regions through \emph{coverage}: a quantity that can be estimated in practice and has a criterion to determine acceptable approximations.
\begin{definition}
The {\bfseries coverage probability} of a posterior estimator at a confidence coefficient $1 - \alpha$ is
\begin{equation}
    \int_{\vtheta}\int_{\vx} p(\vtheta,\vx)~\mathbb{1}\left[\vtheta \in \Theta_{\hat{p}(\vtheta|\vx = \vx)}(1 - \alpha)\right]~\d\vtheta\d\vx,
\end{equation}
where the function
$\Theta_{p(\vtheta\vert\vx)}(1 - \alpha)$ yields the $1 - \alpha$ highest posterior density region
of $\hat{p}(\vtheta\vert\vx)$.
\end{definition}
\begin{definition}
The {\bfseries empirical coverage probability} of a posterior estimator at a confidence coefficient $1 - \alpha$ given a set of $n$ i.i.d. samples $(\vtheta^*,\vx)\sim p(\vtheta,\vx)$
is
\begin{equation}
\frac{1}{n} \sum_{i=1}^n ~\mathbb{1}\left[\vtheta^*_i \in \Theta_{\hat{p}(\vtheta|\vx = \vx_i)}(1 - \alpha)\right].
\end{equation}
\end{definition}
\begin{definition}
The {\bfseries nominal coverage probability} is the coverage probability of the true posterior and is equal to the known confidence level $(1 - \alpha)\cdot 100\%$.
\end{definition}
\begin{definition}
A posterior estimator is deemed acceptable if it {\bfseries has coverage} at the confidence level of interest, i.e., whenever the empirical coverage probability is {\bfseries larger or equal} to the nominal coverage probability.
\end{definition}
\begin{definition}
A {\bfseries conservative estimator} is an estimator that has coverage for {\bfseries all} confidence levels.
\end{definition}
Although coverage is a necessary metric to assess conservativeness, it is limited in its ability to determine the information gain a posterior (approximation) has over its prior. To clarify this point, consider an estimator whose posteriors are identical to the prior. In this case, there is no gain in information and the empirical coverage probability is equal to the nominal coverage probability. For this reason, a complete analysis should be complemented with measures such as the mutual information or expected information gain $\mathbb{E}_{p(\vtheta,\vx)}\left[\log p(\vtheta\vert\vx) - \log p(\vtheta)\right]$.
This work however is concerned with {\bfseries conservative inference} and will therefore limit the analysis to the evaluation of coverage. Finally, it should be noted that coverage is a statement about the credible regions in expectation. Coverage does not make any statement about the quality of a single posterior.

\section{Experimental observations}
\label{sec:experiments}
This section covers our main contribution: the collection of empirical evidence to determine whether approaches in simulation-based inference are conservative by nature.
We are particularly interested in determining \emph{if} certain approaches should be
favoured over others. We do so by measuring the coverage of estimators attained by these approaches across a broad range of hyperparameters and benchmarks of varied complexity, including two \emph{real} problems from the field of astronomy.
As in real use-cases, the true posteriors associated with these benchmarks are unknown.
Hyperparameters are listed in Appendix \ref{appendix:hyperparameters}.
\subsection{Methods}
\label{sec:methods}
We make the distinction between two paradigms.
Non-amortized approaches are designed to approximate a \emph{single} posterior, while amortized methods aim to learn a general purpose estimator that attempts to approximate \emph{all} posteriors supported by the prior.
\subsubsection{Amortized}
{\bf Neural Posterior Estimation} (\npe) is concerned with directly learning an amortized estimator $\hat{p}_\psi(\vtheta\vert \vx)$ to the posterior with normalizing flows. Normalizing flows define a class of probability distributions $p_\psi(\cdot)$ built from neural network based bijective transformations \citep{dinh2014nice,dinh2016density} parameterized by $\psi$ and are usually optimized via
$\argmin_\psi \mathbb{E}_{p(\vx)} \left[\textsc{kl}(p(\vtheta|\vx)~\vert\vert ~\hat{p}_\psi(\vtheta|\vx)\right]$,
which is equivalent to $\argmax_\psi \mathbb{E}_{p(\vtheta,\vx)}\left[\log \hat{p}_\psi(\vtheta|\vx)\right]$.
Once trained, the density of the modeled distribution can easily be evaluated \emph{and} sampled from.

@@

{\bf Ensembles} An ensemble model \emph{averages} the approximated posteriors of $n$ separately trained posterior estimators. While this formulation is natural for \textsc{npe}, averaging likelihood-to-evidence ratios is equivalent, because
\begin{equation}
    \frac{p(\vtheta)}{n} \sum_{i=1}^n \hat{r}_i(\vx \vert \vtheta) = \frac{1}{n}\sum_{i=1}^n \hat{p}_i(\vtheta \vert \vx).
\end{equation}
\subsubsection{Non-amortized}
Rejection {\bf Approximate Bayesian Computation} \textsc{(abc)} \citep{rubin1984,pritchard1999population}
numerically estimates a \emph{single} posterior by collecting samples $\vtheta\sim p(\vtheta)$ whenever
$\vx\sim p(\vx\vert\vtheta)$ is \emph{similar} to $\vx_o$. Similarity is expressed by means of a \emph{distance function} $\rho$. For high-dimensional observables, the probability of simulating an observable $\vx$ such that $\vx = \vx_o$ is extremely small. For this reason, \textsc{abc} uses a \emph{summary statistic} $s$ and an \emph{acceptance threshold} $\epsilon$. Using these components, \textsc{abc} accepts samples into the approximate posterior whenever $\rho(s(\vx),s(\vx_o))\leq\epsilon$. In our experiments we use the identity function as a sufficient summary statistic. Finally, we emphasize that
\textsc{abc} approximations are \emph{only exact} whenever the summary statistic is sufficient \emph{and} the acceptance threshold $\epsilon$ tends to 0 \citep{sisson2018overview}.

@@

\subsection{Results}
\protect\begin{custombox}
{\bfseries Observation 1} All benchmarked algorithms produce non-conservative posterior approximations. This pathology tends to be accentuated when using a small simulation-budget in both amortized and non-amortized approaches.
